{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-05 wacv_for_review.tex
Comments Replied

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background, at least twice, bigger than that of the first filter,
$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
  E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target.

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!b]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}
\begin{figure*}[!h]
\centering
\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is a marginal difference among
  the scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure*}

@@

We, first, use two
conventional features, fHoG \cite{felzenszwalb2010object} and
color-naming \cite{li2014scale}, to make {\it E}nKCF run on any
embedded systems faster than 30 fps. {\it Burak: You need to make
  these two sentences connected -- the one begin with ``We, first,
  use,'' and ``Figure ..''}

Figure \ref{fig:Filters} shows examples of the region of interest
(ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.

We used different features for each of three KCFs to address different
challenges. In particular, the translation filter, $R_{t}^{L}$, uses
both the fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} features to learn the large background area
around the target as shown in Figure~\ref{fig:Filters}. {\it Burak:
  There are three subfigures in Figure \ref{fig:Filters}. You need to
  tell the readers of this paper which one they need to look at if
  they want to.}

The color features compensate for the noisier shape features due to
the large ROI considered by $R_{t}^{L}$. {\it Burak: You meant ``the
  color features are used to compensate for shape features' weakness
  -- what's weakness?}

On the other hand, color features is not assigned to $R_{t}^{S}$ as it
learns more useful shape features than $R_{t}^{L}$ due to smaller
padding size. {\it Burak: color features are not used for $R_{t}^{S}$ because?}

Both fHoG and color-naming features are used for $R_{s}$ to ? {\it
  Burak: DO NOT USE $R_s$ just only, alway use them with their names,
  the scale filter. This would just confuse the reader! Don't expect
  for them to remember what you said earlier!}

since we believe that the lower template resolution (64 x n)
assigned to $R_{s}$ might lead to less discriminative shape
features.

Smaller template size is assigned to $R_{s}$ as it estimates
the scale by correlating the filter with three ROIs as shown in
alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By doing so, we can avoid
fluctuating run-time performance which is not desired in embedded
systems.

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. {\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}
as features for this idea where their experiments showed that the
first convolutional layer features lead to slightly better precision
and success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker with deeper features. Their method employs the
third convolutional layer features to estimate the response map. In
the next stage, they used the estimation of the target's transition
from the first phase to use the second convolutional layer features
and update transition estimation.  Finally, the first convolutional
layer features is extracted from the ROI estimated in the second
stage. This coarse-to-fine position estimation approach accommodates
different levels of abstractions of the object. However, such approach
runs multiple KCFs at a single frame, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF.

Our {\it E}nKCF framework allows us to exploit different level of
feature encodings with different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area than
$R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it relies on less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

We first evaluate the performance of {\it E}nKCF with hand-crafted features.
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way for the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in figure~\ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC) indicating that higher level feature absractions 
works better for the smaller ROIs.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123.

{\it Burak: No summary on EnKCF w/ deep features?}

>>>>

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background, at least twice, bigger than that of the first filter,
$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
  E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target as shown in Figure~\ref{fig:Filters}.

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

\begin{figure*}[!h]
\centering
\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is a marginal difference among
  the scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure*}

@@

We, first, use two hand-crafted features, fHoG \cite{felzenszwalb2010object} 
and color-naming \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps.

In particular, the translation filter, $R_{t}^{L}$, uses
both the fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} features to learn the large background area
around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
compensate for the noisier fHoG features due to the large ROI considered 
by $R_{t}^{L}$. {\it Burak: You meant ``the
  color features are used to compensate for shape features' weakness
  -- what's weakness?}

  {\it YoungWoo : The weakness is the more background you include the noisier
  HoG features become.}
On the other hand, the color features is not assigned to the small area translation 
filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used for $R_{s}$, the scale filter, 
since the lower template resolution (64 x n)
assigned to $R_{s}$ leads to less discriminative shape
features as in Figure~\ref{fig:Filters}.c. Smaller template size is assigned to $R_{s}$ as it estimates
the scale by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By doing so, we can avoid
fluctuating run-time performance among KCFs which is not desired in embedded
systems.

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. {\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}
  {\it YoungWoo : EnkCF with deep features improved the performance on the same set of data.}
This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}
for this idea where their experiments showed that the
first convolutional layer features lead to slightly better precision
and success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction capacity. 
Their method first employs the third convolutional layer features to estimate the response map. In
the next stage, they used the estimation of the target's transition
from the first phase to use the second convolutional layer features
and update transition estimation.  Finally, the first convolutional
layer features is extracted from the ROI estimated in the second
stage. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, such approach
runs multiple KCFs at a single frame, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF.

Our {\it E}nKCF framework allows us to exploit different level of
feature encodings with different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area than
the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it learns less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features.  With this tracker, we aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way in the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in figure~\ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC) indicating that higher level feature absraction
works better for the smaller ROIs.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
To further improve the performance, we employed deeper features to the scale filter as it learns smaller ROI
than the translation filters.
